### 2020-12-16 README.Rmd
added headers
final clean up before making repo public
last few small changes
updated readme

Repository for research journals for my research projects related to LIME. See below for descriptions of the contents of this repository. For easy viewing of the journals, use these links:

0. [Objectives and Ideas](https://goodekat.github.io/LIME-research-journals/journals/00-objectives_and_ideas/00-objectives_and_ideas.html)
1. [Information on Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/01-hamby_data_and_models/01-hamby_data_and_models.html)
2. [Understanding LIME](https://goodekat.github.io/LIME-research-journals/journals/02-understanding_lime/02-understanding_lime.html)
3. [Applying LIME to Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/03-applying_lime/03-applying_lime.html)
4. [Assessing LIME on Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/04-assessing_lime/04-assessing_lime.html)
5. [Applying and Assessing LIME on Iris Data](https://goodekat.github.io/LIME-research-journals/journals/05-iris_comparison/05-iris_comparison.html)
6. [Notes on Readings](https://goodekat.github.io/LIME-research-journals/journals/06-literature_review/06-literature_review.html)
7. [Computational Issues](https://goodekat.github.io/LIME-research-journals/journals/07-computation_issues/07-computation_issues.html)
8. [LIME Applied to Logistic Regressions on Sine Data](https://goodekat.github.io/LIME-research-journals/journals/08-logistic_regression/08-logistic_regression.html)
9. [Identifying rtrees Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying_rtrees_training_data/09-identifying_rtrees_training_data.html)
10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-lime_hamby_variability/10-lime_hamby_variability.html)

@@

[**code**](code/)

@@

[**figures**](figures)

@@

[**journals**](journals)

@@

[**old-journals**](old-journals)

@@

**main**

>>>>

Repository for research journals for my research projects related to LIME. See below for descriptions of the contents of this repository.

Descriptions of the work done can be found in the journals. Beware of typos in the journals. Not all of them have been proof read. For easy viewing of the journals, use these links:

0. [Objectives and Ideas](https://goodekat.github.io/LIME-research-journals/journals/00-objectives_and_ideas/00-objectives_and_ideas.html)
1. [Information on Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/01-hamby_data_and_models/01-hamby_data_and_models.html)
2. [Understanding LIME](https://goodekat.github.io/LIME-research-journals/journals/02-understanding_lime/02-understanding_lime.html)
3. [Applying LIME to Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/03-applying_lime/03-applying_lime.html)
4. [Assessing LIME on Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/04-assessing_lime/04-assessing_lime.html)
5. [Applying and Assessing LIME on Iris Data](https://goodekat.github.io/LIME-research-journals/journals/05-iris_comparison/05-iris_comparison.html)
6. [Notes on Readings](https://goodekat.github.io/LIME-research-journals/journals/06-literature_review/06-literature_review.html)
7. [Computational Issues](https://goodekat.github.io/LIME-research-journals/journals/07-computation_issues/07-computation_issues.html)
8. [LIME Applied to Logistic Regressions on Sine Data](https://goodekat.github.io/LIME-research-journals/journals/08-logistic_regression/08-logistic_regression.html)
9. [Identifying rtrees Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying_rtrees_training_data/09-identifying_rtrees_training_data.html)
10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-lime_hamby_variability/10-lime_hamby_variability.html)
11. [Gower Exponent Examples](https://goodekat.github.io/LIME-research-journals/journals/11-gower-exponent-examples/11-gower-exponent-examples.html)

@@

#### [**code**](code/)

@@

#### [**figures**](figures)

@@

#### [**journals**](journals)

@@

#### [**old-journals**](old-journals)

@@

#### **main**
